Figures

### 2018-07-19 figures/07_cor_mat_hmap.Rmd
figure sizes are reasonable now

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3.7, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}

>>>>

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=4.3, fig.height=4, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}

### 2018-07-19 manuscript/figures.Rmd
figure sizes are reasonable now

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

>>>>

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
```
